    \resumeSubheading
      {Tsuru Robotics}{Moscow, Russia}
      {Junior Research \& Development Engineer}{Jun 2020 -- Present}
      \begin{itemize}[leftmargin=0in, label={}]
            \small{\item{
                {— Developed real-time (40 us) UWB-based Positioning System:}\\
                {—— Developed architecture capable of positioning an infinite amount of devices in the scope of one system.}\\
                {—— Implemented data analysis pipeline in MATLAB for system refinement.}\\
                {——— Mitigated positioning error from over 5m to sub-30cm precision of detection.}\\
                {— Participated in the Drone Show preparation:}\\
                {—— Assembled, tested and deployed 3 power supplies for LED arrays and arrays themselves.}\\
                {—— Assisted in MoCap-based system development of tracking the correctness of an aim in the shooting range.}\\
                {——— The main assumption: an aim has external coordinates (A-GPS), the gun has only MoCap-based  coordinates.}
            }}
      \end{itemize}
    \resumeSubSubheading
    {Embedded Systems Intern}{Mar 2020 -- Jun 2020}
      \begin{itemize}[leftmargin=0in, label={}]
            \small{\item{
                {— Developed real-time (100 us) Time-of-Arrival based Positioning system with Cortex-M4 chip:}\\
                {—— Coded Firmware with C language to enable the system.}\\
                {—— UART/Segger RTT for debugging and logging.}\\
                {— Researched said Positioning system's parameters and error margins.}\\
                {—— MATLAB as a main tool of gathered data analysis.}
            }}
      \end{itemize}