\section{Publications and Conference Patricipations}
\resumeSubHeadingListStart
\resumeProjectHeading
  {A. Tikhomirov, A. Briko, N. Seleznev, \textbf{A. Petrosyants}, S. Shchukin.\\
  \textit{Comparison of Elliptical and Spherical Geometric
  Model of the Heart}\\
  \textit{for Computer Multi-channel Electrical Impedance Cardiography}.}{}
      \begin{itemize}[leftmargin=0in, label={}]
        \small{\item{
          {Ural Symposium on Biomedical Engineering, Radioelectronics and Information Technology (USBEREIT), \\ 
          Yekaterinburg, Russia, 2021.}
          {\textbf{\textit{Accepted.}}}
        }}
      \end{itemize}

\resumeProjectHeading
    {\textbf{A. Petrosyants}, A. Volkov, A. Nikolaev.\\
  \textit{Electrical Impedance Tomography Data Acquisition Emulation}.}{}
      \begin{itemize}[leftmargin=0in, label={}]
      \small{\item{
        {Ural Symposium on Biomedical Engineering, Radioelectronics and Information Technology (USBEREIT), \\ 
              Yekaterinburg, Russia, 2020, pp. 44-47.}
        {\href{https://ieeexplore.ieee.org/abstract/document/9117667/}{\underline{doi: 10.1109/USBEREIT48449.2020.9117667}}}
      }}
      \end{itemize}

  \resumeProjectHeading
      {Yu. Ershov, V. Akopyan, S. Alkov, \textbf{A. Petrosyants}.\\
    \textit{Theoretical Bases of Ultrasonic Phaco-Operation}.}{}
        \begin{itemize}[leftmargin=0in, label={}]
        \small{\item{ 
          {J Tech Living Sys, Tome 14, No.1 2017. pp. 36-39. \href{https://www.elibrary.ru/item.asp?id=29715174}{\underline{ISSN: 2070-0997}}}
            }}
      \end{itemize}

  \resumeProjectHeading
    {\textbf{A. Petrosyants}, V. Akopyan \textit{et al}.\\
  \textit{A Model of Ultrasound Phacodispersion of an Eye Lens}.}{}
      \begin{itemize}[leftmargin=0in, label={}]
     \small{\item{ 
              {Mathematics. Computing. Education. MCE-2017. Pushchino, Russia, Jan 23-28 2017}
      }}
      \end{itemize}

  \resumeProjectHeading
      {V. Akopyan, M. Bambura, \textbf{A. Petrosyants}, S. Alkov, Yu. Ershov.\\
    \textit{An Ultrasonic Injection Device}.}{}
      \begin{itemize}[leftmargin=0in, label={}]
      \small{\item{ 
              {MedTech-2016. Moscow, Russia @ BMSTU,  Nov 22-23 2016}
      }}
      \end{itemize}
\resumeSubHeadingListEnd