\resumeSubheading
  {Research \& Development Engineer}{Moscow, Russia}
  {\href{https://tsuru.su/en/}{\underline{Tsuru Robotics}} | \href{http://flyfire.io/}{\underline{Flyfire}}}{Mar 2020 -- Nov 2021}
  \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
      {$\bullet$ Real-time (up to 25 Hz) \textbf{UWB-based Local Positioning System} (UWBLPS) using \textbf{bare-metal C}:}\\
      {— Developed UWBLPS that supports any amount of drones. It is based on \textbf{time difference of arrival} (TDoA) principle with \textbf{time-division multiple access} (TDMA) collision avoidance.}\\
      {— Developed \textbf{Kalman Filter} and  \textbf{Gradient Descent with momentum} for TDoA, orientation and on-board telemetry to get the coordinates.}\\
      {— Developed firmware for drones' UWBLPS.}\\
      {—— \textbf{UART/Segger RTT} for debugging and logging.}\\
      {—— \textbf{MATLAB} data analysis tools and firmware prototyping. \textbf{Python} for automation.}\\
      {— Achieved faultless \textbf{position hold} with UWBLPS for numerous drones.}\\
      {— Achieved positioning \textbf{error margin of 10-30 cm}, homogeneous across the setup.}\\
      {$\bullet$ Drone Show System}\\
      {— Conducted drones' wind resistivity tests in a certified facility with a wind tunnel.}\\
      {— Conducted drones' luminosity study in a certified facility.}\\
      {— Developed Drone Show System \href{https://bit.ly/3fa2qcd}{\underline{User Manual}} for drones and peripherals.}
    }}
  \end{itemize}